### 2016-04-22 paper.tex
Add base template for paper.

\documentclass{article}

\title{APPM 3310 Project\\\Large{Static Analysis of Truss Systems}}
\author{Sammy Chang\and{}Ryan Marizza\and{}Michael Shannon}
\date{Friday, April 29, 2016}

\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue, citecolor=blue}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}

\usepackage{abstract}
\renewcommand{\abstractname}{}
\renewcommand{\absnamepos}{empty}
\renewcommand{\abstracttextfont}{\normalfont\small\bfseries}

\usepackage[citestyle=authoryear]{biblatex}
\addbibresource{paper.bib}

\begin{document}

\maketitle

\begin{abstract}
    Abstract goes here.
\end{abstract}

\section{Introduction}

\section{Mathematical Formulation}

\section{Examples and Numerical Results}

\section{Discussion}

\section{Conclusion}

\nocite{*}
\printbibliography{}

\end{document}

### 2016-04-24 paper.tex
Write start of "Mathematical Formation" section.
This includes the entire "Element Formation" section.

@@
 \usepackage{graphicx}
+\usepackage{enumitem}
 
@@
 
+Most of the following formulation follows directly from
+\parencite{felippa2004}.
+
+In this paper the accompanying tools use the direct stiffness method.  This
+method is based on using known forces and displacements as well as the modulus
+of elasticity of the structure members to back out displacements.  In this
+way, it is unlike the direct force method which can only solve statically
+determinate systems as the direct stiffness method can solve indeterminate
+systems as well by properly splitting the stress among the truss members.
+
+The direct stiffness method involves 8 steps.  The first two are purely
+conceptual and thus are never really performed and the last one is a post
+processing step performed after a solution is found.  These eight steps are
+outlined below (taken from Figure 2.5 of \cite{felippa2004}).
+\begin{enumerate}[noitemsep]
+    \item Disconnection
+    \item Localization
+    \item Element Formation
+    \item Globalization
+    \item Merge
+    \item Application of Boundary Conditions
+    \item Solution
+    \item Recovery of Derived Quantities
+\end{enumerate}
+
+The disconnection step is essentially just looking at each truss member
+(element) individually while localization is just looking at member based
+coordinate systems.  Therefore, this paper will skip directly to the first
+step requiring actual work, \emph{element formation}.
+
+\subsection{Element Formation}
+
+The eventual goal is to find the master stiffness equation
+\begin{equation}
+    \mathbf{f}=K\mathbf{u} \label{eq:master_stiffness_equation}
+\end{equation}
+where $\mathbf{f}$ is the vector of external forces, $\mathbf{u}$ the vector
+of displacements, and $K$ the linear relation between the two.  This equation
+is in a global coordinate frame.  $K$ is $n\times{}n$ where $n$ is the number
+of nodes (endpoint of one or more members) times the number of dimensions
+which for the remainder of this document will be taken as 2.
+
+Before the master stiffness equation can be written a relation between
+displacement and external force for each element must be developed.  To do
+this, the elements of the truss are treated as springs and therefore governed
+by Hook's law.
+\begin{equation}
+    f=k_su \label{eq:hooks_law}
+\end{equation}
+where $f$ is the force, $u$ is the displacement, and $k_s$ is the stiffness of
+the spring, which for an element of constant cross sectional area $A$, of
+length $L$ and made of a material with elastic modulus $E$ is given by:
+\begin{equation}
+    k_s=\frac{EA}{L} \label{eq:stiffness_coefficient}
+\end{equation}
+
+By making the simplification that nodes cannot impart any torque on elements
+the only equation governing an element is Hook's law.  In the element centered
+coordinate frame the one dimensional Hook's law, Eq.~(\ref{eq:hooks_law}) is
+enough.  However, in order to convert this into the global coordinate frame a
+full dimensional equation is needed.  This equation will be designated as the
+local stiffness equation:
+\begin{equation}
+    \overline{\mathbf{f}}=\overline{K}\overline{\mathbf{u}}
+    \label{eq:local_stiffness_equation}
+\end{equation}
+This equation is in a member centric coordinate frame with the origin placed
+on the first node of the element and the $x$-axis along the element, pointing
+to the 2nd node.  The direction of all other axes are unimportant.  Therefore,
+in the 2-dimensional case $\overline{K}$ becomes:
+\begin{equation}
+    \overline{K}=\frac{EA}{L}\begin{bmatrix*}[r]
+        1&0&-1&0\\
+        0&0&0&0\\
+        -1&0&1&0\\
+        0&0&0&0
+    \end{bmatrix*}
+\end{equation}
+The 3-dimensional case can be easily obtained by adding 2 zero rows and 2 zero
+columns.
+
+\subsection{Globalization}
+
+Before the global stiffness matrix can be formed
+Eq.~(\ref{eq:local_stiffness_equation}) must be converted into the global
+coordinate frame equation:
+\begin{equation}
+    \mathbf{f}^e=K^e\mathbf{u}^e
+\end{equation}
+which relates displacement to force for a single element $e$ in the global
+coordinate frame.  Eq.~(\ref{eq:global_to_local}) shows the relation between the
+global coordinate frame and the local coordinate frame.
+\begin{equation}
+    \overline{\mathbf{u}}^e=T^e\mathbf{u},\qquad
+    \overline{\mathbf{f}}^e=T^e\mathbf{f}
+    \label{eq:global_to_local}
+\end{equation}
+
+\subsection{Merge}
+
+\subsection{Application of Boundary Conditions}
+
+\subsection{Solution}
+
+\subsection{Recovery of Derived Quantities}
+
 \section{Examples and Numerical Results}

### 2016-04-25 paper.tex
Write globalization section.

@@
 full dimensional equation is needed.  This equation will be designated as the
-local stiffness equation:
+local stiffness equation for element $e$:
 \begin{equation}
-    \overline{\mathbf{f}}=\overline{K}\overline{\mathbf{u}}
+    \overline{\mathbf{f}}^e=\overline{K}^e\overline{\mathbf{u}}^e
     \label{eq:local_stiffness_equation}
@@
 to the 2nd node.  The direction of all other axes are unimportant.  Therefore,
-in the 2-dimensional case $\overline{K}$ becomes:
+in the 2-dimensional case $\overline{K}^e$ becomes:
 \begin{equation}
-    \overline{K}=\frac{EA}{L}\begin{bmatrix*}[r]
+    \overline{K}^e=\frac{EA}{L}\begin{bmatrix*}[r]
         1&0&-1&0\\
@@
         0&0&0&0
-    \end{bmatrix*}
+    \end{bmatrix*} \label{eq:kbar}
 \end{equation}
@@
 \begin{equation}
-    \mathbf{f}^e=K^e\mathbf{u}^e
+    \mathbf{f}^e=K^e\mathbf{u}^e\label{eq:global_stiffness_equation}
 \end{equation}
 which relates displacement to force for a single element $e$ in the global
-coordinate frame.  Eq.~(\ref{eq:global_to_local}) shows the relation between the
-global coordinate frame and the local coordinate frame.
+coordinate frame.  Let $\mathbf{x}$ be a vector in the global coordinate
+system and $\overline{\mathbf{x}}$ be the equivalent vector in the element
+local coordinate frame.  Then the relation between the two is given by
+\parencite{olver2006}:
+\begin{equation}
+    S\overline{\mathbf{x}}=\mathbf{x}\qquad\text{where}\qquad
+    S=\left\{\mathbf{v}_1,\mathbf{v}_2,\ldots,\mathbf{v}_n\right\}
+\end{equation}
+With the $\mathbf{v}$ vectors forming a basis for the element centered
+coordinate system.  In particular, $v_1$ is the unit vector along the element.
+If the other columns of $S$ are chosen such that $S$ is orthonormal then
+$S^{-1}=S^{T}$.  Therefore, the reverse transformation is:
+\begin{equation}
+    \overline{\mathbf{x}}=S^{-1}\mathbf{x}=S^T\mathbf{x}
+\end{equation}
+Noting that $\mathbf{u}$ and $\mathbf{f}$ are stacked vectors that rotate
+though each coordinate twice the appropriate transformation matrix for element
+$e$ becomes:
+\begin{equation}
+    T^e=\begin{pmatrix}
+        S^T&O\\O&S^T
+    \end{pmatrix}
+\end{equation}
+Therefore, Eq.~(\ref{eq:global_to_local}) shows the relation between the
+global coordinate frame and the local coordinate frame for the force and
+displacement vectors.
 \begin{equation}
@@
     \label{eq:global_to_local}
+\end{equation}
+By combining Eq.~(\ref{eq:local_stiffness_equation},
+\ref{eq:global_stiffness_equation}, \ref{eq:global_to_local}) the global
+stiffness matrix (for element $e$), $K^e$ can be related to the local
+stiffness matrix $\overline{K}^e$ by:
+\begin{equation}
+    K^e=(T^e)^T\overline{K}^eT^e
 \end{equation}

### 2016-04-25 paper.tex
Add merge section.

@@
 \usepackage{enumitem}
+\usepackage{listings}
 
@@
 Most of the following formulation follows directly from
-\parencite{felippa2004}.
+\parencite{felippa2004ch2} and \parencite{felippa2004ch3}.
 
@@
 processing step performed after a solution is found.  These eight steps are
-outlined below (taken from Figure 2.5 of \cite{felippa2004}).
+outlined below (taken from Figure 2.5 of \cite{felippa2004ch2}).
 \begin{enumerate}[noitemsep]
@@
 
-Before the global stiffness matrix can be formed
+Before the master stiffness matrix can be formed,
 Eq.~(\ref{eq:local_stiffness_equation}) must be converted into the global
@@
 
+The master stiffness equation Eq.~(\ref{eq:master_stiffness_equation}) relates
+the displacement of every node, stored in $\mathbf{u}$ to every external force
+in vector $\mathbf{f}$ using the linear transformation $K$.  The assembly of
+each $K^e$ into $K$ is governed by \parencite{felippa2004ch3}:
+\begin{enumerate}[noitemsep]
+    \item Compatibility of displacements at any given node.
+    \item Equilibrium of internal and external forces.
+\end{enumerate}
+The typical method of handling assembly of the global stiffness equations,
+Eq.~(\ref{eq:global_stiffness_equation}), is to sum the forces and sum the
+$K^e$ matrices by first expanding them to the size of $K$ by adding rows and
+columns of zeros in the appropriate locations.  In the case of the computer
+code that accompanies this document \parencite{shannon2016} the method in
+section 3.5.1 of \cite{felippa2004ch3} is used.  This is know as
+\emph{Assembly by Freedom Pointers}.  The algorithm is governed by
+Eq.~(\ref{eq:global_to_master}) copied from \cite{felippa2004ch3} and fills $K$
+by iterating through each element $e$ and then through the values in $K^e$
+where $d=4$ in the 2-dimensional case and $d=6$ in the 3-dimensional case.
+Let the number of elements in the truss be given by $m$.
+
+\begin{minipage}{\textwidth}
+\begin{equation*}
+    K_{pq}=\sum_{e=1}^{m}K_{ij}^e
+\end{equation*}
+\begin{equation}
+    \text{for}\label{eq:global_to_master}
+\end{equation}
+\begin{equation*}
+    i=1,2,\ldots,d,\quad{}j=1,2,\ldots,d\qquad{}
+    p=EFT^e(i),\quad{}q=EFT^e(j)
+\end{equation*}
+\vspace{0.1em}
+\end{minipage}
+
+The \emph{element freedom table} ($EFT^e$) is unique for each element $e$ and
+gives the row/column indices where the values in $K^e$ are to be added into
+$K$.  The specific algorithm to get $EFT^e$ is better explained in code and
+can be found at \lstinline$libs/element_freedom_table.m$ in
+\cite{shannon2016}.  In reality, $K$ is initialized to the zero matrix.  The
+force vector $\mathbf{f}$ is simply constructed by summing the known (applied)
+external forces in the proper indices which can also be obtained from the
+\emph{element freedom table}.
+
 \subsection{Application of Boundary Conditions}

### 2016-04-25 paper.tex
Add boundary condition and solution sections.

@@
 
+Eq.~(\ref{eq:master_stiffness_equation}) is singular because while the truss
+is \emph{hopefully} self constrained at this point it is not constrained in
+space.  This is because Eq.~(\ref{eq:master_stiffness_equation}) does not yet
+take into acount the fact that $\mathbf{u}$ is under some restrictions due to
+constraints on the physical truss.  For the purpose of this paper, and the
+accompanying software \parencite{shannon2016}, constraints will be limited to
+one of the principal ($xyz$) dimensions.  Therefore, some of the entries of
+$\mathbf{u}$ are forced to be zero and in these locations the force is
+unknown.  The normal way to handle this is to simply remove the associated
+rows and columns from $\mathbf{f}$, $\mathbf{u}$, and $K$.  However, in a
+software package this either requires special logic when implementing
+Eq.~(\ref{eq:global_to_master}) or requires reallocating a new $K$ matrix
+after the fact.
+
+Therefore, in this paper the computer friendly method outlined in section
+3.5.2 of \cite{felippa2004ch3} is used.  This method involves setting the
+diagonals of $K$ that correspond to the constrained parts of $\mathbf{u}$ to 1
+and the corresponding values in $\mathbf{f}$ to 0.  This forces those elements
+of $\mathbf{u}$ to solve to 0 displacement.  This is a simple $O(n)$ operation
+instead of the higher order delete of rows and columns.
+
 \subsection{Solution}
+
+Finally, Eq.~(\ref{eq:master_stiffness_equation}) is non-singular and thus can
+be solved by any number of methods.  The result is the column vector of
+displacements $\mathbf{u}$.  This gives the displacements of each node and
+therefore the displacement of the endpoints of each element.  This is enough
+to plot the new layout of the truss under load.
 
@@
 
-\nocite{*}
+% \nocite{*}
 \printbibliography{}

### 2016-04-25 paper.tex
Add abstract from Sammy Chang.

@@
 \begin{abstract}
-    Abstract goes here.
+This report covers application of Linear Algebra in the Finite Element Method.
+More specifically we delve into the Direct Stiffness Method (DSM) which is one
+common method to apply FEM. Our code is able to solve 2D and 3D truss systems
+using DSM. DSM is essentially based on three knowns: forces, displacements and
+elastic modulus'. The scope of the project only covers 2D trusses, but the
+code does have the ability to solve 3D systems.
 \end{abstract}

### 2016-04-25 paper.tex
Add Introduction from Sammy Chang.

@@
 \section{Introduction}
+The truss analyzer implements the DSM by simplifying and idealizing a given
+truss system. By that, all of the joints are converted to frictionless pin
+joins, and we will ignore the bending of individual truss members. Our
+idealization for most cases is satisfactory for an elementary truss analysis.
+Therefore we will only be observing the axial forces and the displacements at
+the pin joints. Our truss analyzer "converts" the pins and members to a node
+and an element, respectively under the Cartesian coordinate system.
+Furthermore, we are able to apply external forces only at the joints. This
+will allow us to simulate displacement in all the nodes of the truss system.
+The analyzer works by inputting a truss system, the code then identifies
+individual elements. When the elements are identified, the truss system is
+disassembled at the nodes. The elements are further analyzed using stiffness
+equations dependent on the geometry and the elastic moduli of the elements.
+Once those elements have been analyzed, the code re-assembles the structure
+with the stiffness of the elements. The element stiffness matrix is then
+modified by applying the displacements and externally applied forces at the
+nodes. A final matrix is obtained (global stiffness matrix) which can be
+solved using the displacement and force vectors by applying the Cholesky
+decomposition. Using DSM allows us to analyze complex truss structures as well
+as statically indeterminate structures.
 

### 2016-04-25 paper.tex
Write post processing section.

@@
 \author{Sammy Chang\and{}Ryan Marizza\and{}Michael Shannon}
-\date{Friday, April 29, 2016}
+\date{Section: 002\\\vspace{1em}Friday, April 29, 2016}
 
@@
 
+While the deformation for the truss is known at this point the stresses in the
+elements are the desired quantity to determine if the goal is to determine if
+the truss will break.  The first step is to find the change in length of each
+element.  This is done by extracting the displacement values from $\mathbf{u}$
+for each element reforming each $\mathbf{u}^e$.
+Eq.~(\ref{eq:global_to_local}) is then used to move the displacement back into
+the element local coordinate frame.  At this point only the two x-coordinate
+displacement values (at each end of the element) are nonzero as an element can
+only deform along its axis (given the simplifications used in this paper).
+Subtracting one from the other gives the change in length
+\parencite{felippa2004ch3}:
+\begin{equation}
+    d^e=\overline{\mathbf{u}}^e_{xj}-\overline{\mathbf{u}}^e_{xi}
+\end{equation}
+where $j$ is the 2nd node of the element and $i$ is the first.  Using this
+result the longitudinal stress and force in the element is given by:
+\begin{equation}
+    \sigma^e=\frac{E^e}{L^e}d^e,\qquad
+    F^e=\sigma^eA^e
+\end{equation}
+At this point, both the truss deformation and element stresses are known and
+therefore the figures shown in this paper can be plotted.
+
 \section{Examples and Numerical Results}

### 2016-04-26 paper.tex
Add Conclusion from Ryan Marizza.

@@
 
+The truss analyzer is able to properly analyze a complex truss system based on
+three known values: forces, displacements, and elastic moduli using
+calculations based on these values and structure geometry. The analysis is
+able to break down a truss system and implement the DSM by idealizing the
+truss system, and simplifying complex real world phenomena into a manageable
+set of linear stiffness equations. These stiffness equations are used to
+describe the structure's elements, each of which can be subjected to an
+external force/displacement at a node. From this, a global stiffness matrix is
+produced and solved using the force vectors and displacement vectors. This DSM
+truss analysis can be used for complex structures and is useful when it comes
+to structures with many distinct nodes, each with distinct forces and
+displacements. Solving for the stresses on these nodes without the use of
+linear algebra is nearly impossible. Through this DSM analysis, using linear
+algebraic methods, important engineering structures, notably: bridges, wings,
+buildings, can be analyzed. Knowing the stresses on elements of these
+structures allows engineers to predict behavior of structures under force.
+Such behaviors that can be predicted are elastic deformation, plastic
+deformation, crack growth, crack propagation, and structural failure. From
+this it is easy to see why such structure analysis is important.
+
 % \nocite{*}

### 2016-04-26 paper.tex
Add Discussion section from Ryan Marizza.

@@
 
+Truss analysis using DSM ignores many real world phenomena and has many
+limitations in terms of complexity for the sake of simplicity. A more
+realistic, yet much more complicated FEM tool could be created to analyze a
+truss system taking into account more real world phenomena and allowing for
+much more information to be imputed about the truss system. Such
+simplifications that are made by the DSM analysis are as follows: friction is
+ignored, the bending of truss members is ignored, the cross sectional area of
+each truss element is assumed to be constant, nodes do not impart torque on
+elements, and forces can only be applied at nodes. Understanding of FEM could
+be furthered by creating a more realistic truss system analyzer that takes
+these phenomena into account and allows for forces to be applied at non-node
+locations.
+
 \section{Conclusion}

### 2016-04-26 plot.sh
Add plotting code.

@@ -1,0 +1,26 @@
+#!/bin/sh
+
+MATLAB="matlab-desktop -nodesktop -nosplash"
+
+rm -rf images
+mkdir images
+
+$MATLAB << EOF
+    addpath('code');
+    truss('code/samples/sample_001.json', '-p', '-s');
+    save_figure('images/sample_001.pdf');
+    close all;
+    truss('code/samples/baltimore_truss.json', '-p', '-s');
+    save_figure('images/baltimore_truss.pdf');
+    close all;
+    truss('code/samples/sample_002.json', '-p', '-s');
+    save_figure('images/sample_002.pdf');
+    close all;
+    truss('code/samples/sample_003.json', '-p', '-s');
+    save_figure('images/sample_003.pdf');
+    close all;
+    truss('code/samples/sample_004.json', '-p', '-s');
+    save_figure('images/sample_004.pdf');
+    close all;
+    exit
+EOF

### 2016-04-28 paper.tex
Add figures and fixes.

--- 2016-04-25 paper.tex
@@
 \usepackage{listings}
+\usepackage{float}
 
@@
 
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/sample_001.pdf}
+        \caption{Truss Analyzer on a single truss member with one external
+        force.}
+    \end{center}
+\end{figure}
+
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=1\textwidth]{images/baltimore_truss.pdf}
+        \caption{The DSM application of FEM on a much more complicated system
+        (a Baltimore truss bridge) with 11 applied forces. This example
+        clearly depicts the practical power of such analysis.}
+    \end{center}
+\end{figure}
+
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/sample_002.pdf}
+        \caption{3D analysis of a single truss with one applied force in the
+        same plane as the truss system.}
+    \end{center}
+\end{figure}
+
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/sample_003.pdf}
+        \caption{The DSM application of FEM on a full three dimensional truss
+        with multiple forces in three dimensions.}
+    \end{center}
+\end{figure}
+
+\begin{figure}[H]
+    \begin{center}
+        \includegraphics[width=0.8\textwidth]{images/sample_004.pdf}
+        \caption{The DSM application of FEM on an overconstrained truss
+        system.}
+    \end{center}
+\end{figure}
+
 \section{Discussion}
 
+Truss analysis using DSM ignores many real world phenomena and has many
+limitations in terms of complexity for the sake of simplicity. A more
+realistic, yet much more complicated FEM tool could be created to analyze a
+truss system taking into account more real world phenomena and allowing for
+much more information to be imputed about the truss system. For example we
+assume all nodes or joints, are connected by a pin joint. Such is not true for
+many bridges, as they may be connected with gusset plates or may be non rigid
+cables. The simplifications and assumptions that are made by the truss
+analyzer are as follows: friction is ignored, the bending of truss members is
+ignored, the cross sectional area of each truss element is assumed to be
+constant, nodes do not impart torque on elements, and forces can only be
+applied at nodes. On the flip side, our simple truss analyzer is powerful in
+the way that it can solve both 2D and 3D truss systems, although manual
+implementation of the input code would be extremely tedious for 3D systems.
+
 \section{Conclusion}
+
+The truss analyzer is able to properly analyze a complex truss system based on
+three known values: forces, displacements, and elastic moduli. Using
+calculations based on these values and structure geometry. The script is able
+to break down a truss system and implement the DSM by idealizing the truss
+system, and simplifying complex real world phenomena into a manageable set of
+linear stiffness equations. These stiffness equations are used to describe the
+structure's elements, each of which can be subjected to an external force and
+a displacement at a node. From this, a global stiffness matrix is created and
+solved using the force vectors and displacement vectors. This DSM truss
+analysis can be used for complex truss structures, for a very preliminary
+design analysis. Solving for the stresses on these nodes without the use of
+linear algebra is nearly impossible and/or extremely tedious. Through this DSM
+analysis, using linear algebraic methods, more complex structures, notably:
+bridges, wings, buildings, can be analyzed. Knowing the stresses on elements
+of these structures allows engineers to predict behavior of structures under
+force. Such behaviors that can be predicted are elastic deformation, plastic
+deformation, crack growth, crack propagation, and structural failure, from
+this it is easy to see why such structure analysis is important.
 

### 2016-04-28 plot.sh

@@ -8,19 +8,24 @@ mkdir images
 $MATLAB << EOF
     addpath('code');
     truss('code/samples/sample_001.json', '-p', '-s');
-    save_figure('images/sample_001.pdf');
+    pause(1);
+    save_figure('images/sample_001.pdf', 1);
     close all;
     truss('code/samples/baltimore_truss.json', '-p', '-s');
-    save_figure('images/baltimore_truss.pdf');
+    pause(1);
+    save_figure('images/baltimore_truss.pdf', 1);
     close all;
     truss('code/samples/sample_002.json', '-p', '-s');
-    save_figure('images/sample_002.pdf');
+    pause(1);
+    save_figure('images/sample_002.pdf', 1);
     close all;
     truss('code/samples/sample_003.json', '-p', '-s');
-    save_figure('images/sample_003.pdf');
+    pause(1);
+    save_figure('images/sample_003.pdf', 1);
     close all;
     truss('code/samples/sample_004.json', '-p', '-s');
-    save_figure('images/sample_004.pdf');
+    pause(1);
+    save_figure('images/sample_004.pdf', 1);
     close all;
     exit
 EOF

### 2016-04-28 paper.tex
Add code and input files.

@@
 \usepackage{enumitem}
+\usepackage{float}
+\usepackage{appendix}
+\usepackage{geometry}
+
+\usepackage{bera}
 \usepackage{listings}
-\usepackage{float}
+\usepackage{xcolor}
+\colorlet{punct}{red!60!black}
+\definecolor{background}{HTML}{EEEEEE}
+\definecolor{delim}{RGB}{20,105,176}
+\colorlet{numb}{magenta!60!black}
+\lstdefinelanguage{json}{
+    basicstyle=\normalfont\ttfamily,
+    numbers=left,
+    numberstyle=\scriptsize,
+    stepnumber=1,
+    numbersep=8pt,
+    showstringspaces=false,
+    breaklines=true,
+    frame=lines,
+    backgroundcolor=\color{background},
+    literate=
+     *{0}{{{\color{numb}0}}}{1}
+      {1}{{{\color{numb}1}}}{1}
+      {2}{{{\color{numb}2}}}{1}
+      {3}{{{\color{numb}3}}}{1}
+      {4}{{{\color{numb}4}}}{1}
+      {5}{{{\color{numb}5}}}{1}
+      {6}{{{\color{numb}6}}}{1}
+      {7}{{{\color{numb}7}}}{1}
+      {8}{{{\color{numb}8}}}{1}
+      {9}{{{\color{numb}9}}}{1}
+      {:}{{{\color{punct}{:}}}}{1}
+      {,}{{{\color{punct}{,}}}}{1}
+      {\{}{{{\color{delim}{\{}}}}{1}
+      {\}}{{{\color{delim}{\}}}}}{1}
+      {[}{{{\color{delim}{[}}}}{1}
+      {]}{{{\color{delim}{]}}}}{1},
+}
+\usepackage[framed, numbered]{matlab-prettifier}
 
@@
 
+\newgeometry{top=1in, bottom=1in, left=1in, right=1in}
+\begin{appendices}
+
+\section{Code}
+
+This is the code from \cite{shannon2016}.
+
+\subsection{config.m}\label{app:config.m}
+\lstinputlisting[style=Matlab-editor]{code/config.m}
+
+\subsection{lint.m}\label{app:lint.m}
+\lstinputlisting[style=Matlab-editor]{code/lint.m}
+
+\subsection{save\_figure.m}\label{app:save_figure.m}
+\lstinputlisting[style=Matlab-editor]{code/save_figure.m}
+
+\subsection{save\_tables.m}\label{app:save_tables.m}
+\lstinputlisting[style=Matlab-editor]{code/save_tables.m}
+
+\subsection{truss.m}\label{app:truss.m}
+\lstinputlisting[style=Matlab-editor]{code/truss.m}
+
+\subsection{libs/colormap\_lookup.m}\label{app:libs/colormap_lookup.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/colormap_lookup.m}
+
+\subsection{libs/draw\_arrow.m}\label{app:libs/draw_arrow.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/draw_arrow.m}
+
+\subsection{libs/element\_freedom\_table.m}\label{app:libs/element_freedom_table.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/element_freedom_table.m}
+
+\subsection{libs/force\_vector.m}\label{app:libs/force_vector.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/force_vector.m}
+
+\subsection{libs/global\_stiffness\_matrix.m}\label{app:libs/global_stiffness_matrix.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/global_stiffness_matrix.m}
+
+\subsection{libs/load\_model.m}\label{app:libs/load_model.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/load_model.m}
+
+\subsection{libs/local\_stiffness\_matrix.m}\label{app:libs/local_stiffness_matrix.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/local_stiffness_matrix.m}
+
+\subsection{libs/master\_stiffness\_matrix.m}\label{app:libs/master_stiffness_matrix.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/master_stiffness_matrix.m}
+
+\subsection{libs/modify\_stiffness\_matrix.m}\label{app:libs/modify_stiffness_matrix.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/modify_stiffness_matrix.m}
+
+\subsection{libs/parse\_json.m}\label{app:libs/parse_json.m}
+\url{http://www.mathworks.com/matlabcentral/fileexchange/20565-json-parser}
+
+\subsection{libs/plot\_model.m}\label{app:libs/plot_model.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/plot_model.m}
+
+\subsection{libs/solve\_displacements.m}\label{app:libs/solve_displacements.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/solve_displacements.m}
+
+\subsection{libs/solve\_forces.m}\label{app:libs/solve_forces.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/solve_forces.m}
+
+\subsection{libs/solve\_model.m}\label{app:libs/solve_model.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/solve_model.m}
+
+\subsection{libs/solve\_stresses.m}\label{app:libs/solve_stresses.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/solve_stresses.m}
+
+\subsection{libs/transformation\_matrix.m}\label{app:libs/transformation_matrix.m}
+\lstinputlisting[style=Matlab-editor]{code/libs/transformation_matrix.m}
+
+\section{Input Files}
+
+\subsection{samples/sample\_001.json}\label{app:samples/sample_001.json}
+\lstinputlisting[language=json]{code/samples/sample_001.json}
+
+\subsection{samples/sample\_002.json}\label{app:samples/sample_002.json}
+\lstinputlisting[language=json]{code/samples/sample_002.json}
+
+\subsection{samples/sample\_003.json}\label{app:samples/sample_003.json}
+\lstinputlisting[language=json]{code/samples/sample_003.json}
+
+\subsection{samples/sample\_004.json}\label{app:samples/sample_004.json}
+\lstinputlisting[language=json]{code/samples/sample_004.json}
+
+\subsection{samples/baltimore\_truss.json}\label{app:samples/baltimore_truss.json}
+\lstinputlisting[language=json]{code/samples/baltimore_truss.json}
+
+\section{Output Files}
+
+\end{appendices}
+
 \end{document}

### 2016-04-28 solve.sh
Add CSV table generation.

@@ -5,27 +5,35 @@ MATLAB="matlab-desktop -nodesktop -nosplash"
 rm -rf images
 mkdir images
 
+rm -rf tables
+mkdir tables
+
 $MATLAB << EOF
     addpath('code');
-    truss('code/samples/sample_001.json', '-p', '-s');
+    model = truss('code/samples/sample_001.json', '-p', '-s');
     pause(1);
     save_figure('images/sample_001.pdf', 1);
+    save_tables('tables/sample_001', model);
     close all;
-    truss('code/samples/baltimore_truss.json', '-p', '-s');
+    model = truss('code/samples/baltimore_truss.json', '-p', '-s');
     pause(1);
     save_figure('images/baltimore_truss.pdf', 1);
+    save_tables('tables/baltimore_truss', model);
     close all;
-    truss('code/samples/sample_002.json', '-p', '-s');
+    model = truss('code/samples/sample_002.json', '-p', '-s');
     pause(1);
     save_figure('images/sample_002.pdf', 1);
+    save_tables('tables/sample_002', model);
     close all;
-    truss('code/samples/sample_003.json', '-p', '-s');
+    model = truss('code/samples/sample_003.json', '-p', '-s');
     pause(1);
     save_figure('images/sample_003.pdf', 1);
+    save_tables('tables/sample_003', model);
     close all;
-    truss('code/samples/sample_004.json', '-p', '-s');
+    model = truss('code/samples/sample_004.json', '-p', '-s');
     pause(1);
     save_figure('images/sample_004.pdf', 1);
+    save_tables('tables/sample_004', model);
     close all;
     exit
 EOF

### 2016-04-28 paper.tex
Finish writing appendix.

@@
 \usepackage{geometry}
+\usepackage{csvsimple}
+\usepackage[table]{xcolor}
+\usepackage{fancyhdr}
 
@@
 \usepackage{listings}
-\usepackage{xcolor}
 \colorlet{punct}{red!60!black}
@@
 \begin{document}
+\pagestyle{fancy}
 
@@
 
-\section{Code}
+\newpage
+\section{Input Files}\label{app:input_files}
+
+\subsection{samples/sample\_001.json}\label{app:samples/sample_001.json}
+\lstinputlisting[language=json]{code/samples/sample_001.json}
+
+\subsection{samples/sample\_002.json}\label{app:samples/sample_002.json}
+\lstinputlisting[language=json]{code/samples/sample_002.json}
+
+\subsection{samples/sample\_003.json}\label{app:samples/sample_003.json}
+\lstinputlisting[language=json]{code/samples/sample_003.json}
+
+\subsection{samples/sample\_004.json}\label{app:samples/sample_004.json}
+\lstinputlisting[language=json]{code/samples/sample_004.json}
+
+\subsection{samples/baltimore\_truss.json}\label{app:samples/baltimore_truss.json}
+\lstinputlisting[language=json]{code/samples/baltimore_truss.json}
+
+\newpage
+\section{Output Files}\label{app:output_files}
+
+Output tables of solved truss models in Appendix \ref{app:input_files}.
+
+\csvstyle{nodeTableStyle}{tabular=| r r r r r r r |,
+    table head=\hline \rowcolor{brown!50} \bfseries Node \# &
+        \bfseries x & \bfseries y & \bfseries z &
+        \bfseries dx & \bfseries dy & \bfseries dz,
+    late after head=\\\hline\hline,
+    head to column names,
+    before table=\rowcolors{2}{white!25}{gray!50},
+    late after last line={\\\hline}}
+
+\csvstyle{elementTableStyle}{tabular=| r r r r r r |,
+    table head=\hline \rowcolor{brown!50} \bfseries Element \# &
+        \bfseries Material & \bfseries Node 1 & \bfseries Node 2 &
+        \bfseries Stress & \bfseries Force,
+    late after head=\\\hline\hline,
+    head to column names,
+    before table=\rowcolors{2}{white!25}{gray!50},
+    late after last line={\\\hline}}
+
+\subsection{sample\_001}\label{app:tables/sample_001}
+
+\noindent
+\csvreader[nodeTableStyle]{tables/sample_001_nodes.csv}{}
+    {\node & \x & \y & \z & \dx & \dy & \dz}%
+\vspace{1em}
+
+\noindent
+\csvreader[elementTableStyle]{tables/sample_001_elements.csv}{}
+    {\element & \material & \firstnode & \secondnode & \stress & \force}%
+\vspace{1em}
+
+\subsection{sample\_002}\label{app:tables/sample_002}
+
+\noindent
+\csvreader[nodeTableStyle]{tables/sample_002_nodes.csv}{}
+    {\node & \x & \y & \z & \dx & \dy & \dz}%
+\vspace{1em}
+
+\noindent
+\csvreader[elementTableStyle]{tables/sample_002_elements.csv}{}
+    {\element & \material & \firstnode & \secondnode & \stress & \force}%
+\vspace{1em}
+
+\subsection{sample\_003}\label{app:tables/sample_003}
+
+\noindent
+\csvreader[nodeTableStyle]{tables/sample_003_nodes.csv}{}
+    {\node & \x & \y & \z & \dx & \dy & \dz}%
+\vspace{1em}
+
+\noindent
+\csvreader[elementTableStyle]{tables/sample_003_elements.csv}{}
+    {\element & \material & \firstnode & \secondnode & \stress & \force}%
+\vspace{1em}
+
+\subsection{sample\_004}\label{app:tables/sample_004}
+
+\noindent
+\csvreader[nodeTableStyle]{tables/sample_004_nodes.csv}{}
+    {\node & \x & \y & \z & \dx & \dy & \dz}%
+\vspace{1em}
+
+\noindent
+\csvreader[elementTableStyle]{tables/sample_004_elements.csv}{}
+    {\element & \material & \firstnode & \secondnode & \stress & \force}%
+\vspace{1em}
+
+\subsection{baltimore\_truss}\label{app:tables/baltimore_truss}
+
+\noindent
+\csvreader[nodeTableStyle]{tables/baltimore_truss_nodes.csv}{}
+    {\node & \x & \y & \z & \dx & \dy & \dz}%
+\vspace{1em}
+
+\noindent
+\csvreader[elementTableStyle]{tables/baltimore_truss_elements.csv}{}
+    {\element & \material & \firstnode & \secondnode & \stress & \force}%
+\vspace{1em}
+
+\newpage
+\section{Code}\label{app:code}
 
@@
 
-\section{Input Files}
-
-\subsection{samples/sample\_001.json}\label{app:samples/sample_001.json}
-\lstinputlisting[language=json]{code/samples/sample_001.json}
-
-\subsection{samples/sample\_002.json}\label{app:samples/sample_002.json}
-\lstinputlisting[language=json]{code/samples/sample_002.json}
-
-\subsection{samples/sample\_003.json}\label{app:samples/sample_003.json}
-\lstinputlisting[language=json]{code/samples/sample_003.json}
-
-\subsection{samples/sample\_004.json}\label{app:samples/sample_004.json}
-\lstinputlisting[language=json]{code/samples/sample_004.json}
-
-\subsection{samples/baltimore\_truss.json}\label{app:samples/baltimore_truss.json}
-\lstinputlisting[language=json]{code/samples/baltimore_truss.json}
-
-\section{Output Files}
-
 \end{appendices}
